Boundary Labeling for annotated documents

### 2017-11-15 LaTeX/Paper.tex
Added Pseudocode.tex, esperimented a bit with it.
Paper: Added Supervisor names, re-wrote imprecise parts of terminology section, started work on picture to aid terminology explanation. Program: No changes.

\documentclass[11pt,a4paper]{vutinfth}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amssymb}
%\usepackage{wrapfig}

%TODO: CHANGE!
\setauthor{}{Jakob Klinger}{}{male}
\setadvisor{}{}{}{}%{Pretitle}{Forename Surname}{Posttitle}{male}
%Ass.Prof. Dipl.-Inform. Dr.rer.nat. Martin Nöllenburg
% University Assistant, M.Sc., B.Sc. Fabian Klute

@@

\section{Terminology and Fundamentals} %Evtl in Introduction eingliedern?
While Boundary Labeling (or an equivalent concept) can be applied to a space with different geometry or more dimensions, this paper will only concern itself with two-dimensonal, euclidean space.
To easily reference important concepts, some additional terminology will be introduced as well. (See Fig.~\ref{fig:term} for a visual explanation)%Add references to all terminology pictures!

@@

A \emph{graph} $G=\langle V, E \rangle$ is a tuple of \emph{vertices} $V=\{v_1, v_2, ..., v_n\}$ and \emph{edges} $E=\{e_1, e_2, ..., e_m\}$. A vertex $v$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e$ is a relation between two vertices $E:V\rightarrow  V\times V$. %Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
We call two vertices $u,v \in V$ \emph{adjacent}, if the edge $e=(u,v) \in E$.
 A \emph{path} $P=v_1, ..., v_h$ is an ordered series of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v \in V$ and explores the graph by traversing its edges as far as possible before backtracking. In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{polylines} are a connected series of \emph{Line segments}. Line segments are straight lines that contain each point between their starting and end point. %Open vs. closed line segments?
\emph{labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is an area designated to hold labels and is located off to a side so the labels don't obscure anything.
The point or object that this information refers to is called a \emph{site}. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the leader from Fig~\ref{fig:term} would be classified as an OPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

>>>>

\documentclass[11pt,a4paper]{vutinfth}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\usepackage{wrapfig}

%TODO: CHANGE!
\setauthor{}{Jakob Klinger}{}{male}
\setadvisor{Ass.Prof. Dipl.-Inform. Dr.rer.nat}{Martin Nöllenburg}{}{male}%{Pretitle}{Forename Surname}{Posttitle}{male}
\setfirstassistant{Univ.Ass.}{Fabian Klute}{ M.Sc., B.Sc.}{male}
%Ass.Prof. Dipl.-Inform. Dr.rer.nat. Martin Nöllenburg
% University Assistant, M.Sc., B.Sc. Fabian Klute

@@

\section{Terminology and Fundamentals} %Evtl in Introduction eingliedern?
While Boundary Labeling (or an equivalent concept) can be applied to a space with different geometry or more dimensions, this paper will only concern itself with two-dimensonal, Euclidean space.
To easily reference important concepts, some additional terminology will be introduced as well. (See Fig.~\ref{fig:term} for a visual explanation)%Add references to all terminology pictures!

@@

A \emph{graph} $G=\langle V, E \rangle$ is a tuple of \emph{vertices} $V=\{v_1, v_2, ..., v_n\}$ and \emph{edges} $E=\{e_1, e_2, ..., e_m\}$. A vertex $v$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e$ is a relation between two vertices $E \subseteq V\times V$. %Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
We call two vertices $u,v \in V$ \emph{adjacent}, if the edge $e=(u,v) \in E$.
 A \emph{path} $P=v_1, ..., v_h$ is an ordered sequence of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v \in V$ and explores the graph by traversing its edges as far as possible before backtracking. In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is a rectangular area designated to hold labels. It is located next to of the bigger \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the leader from Fig~\ref{fig:term} would be classified as an OPO-Leader.%Re-write once picture is updated
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

%\begin{algorithm}
%\caption{My algorithm}\label{euclid}
%\begin{algorithmic}[1]
%\Procedure{MyProcedure}{}
%\State $\textit{stringlen} \gets \text{length of }\textit{string}$
%\State $i \gets \textit{patlen}$
%\BState \emph{top}:
%\If {$i > \textit{stringlen}$} \Return false
%\EndIf
%\State $j \gets \textit{patlen}$
%\BState \emph{loop}:
%\If {$\textit{string}(i) = \textit{path}(j)$}
%\State $j \gets j-1$.
%\State $i \gets i-1$.
%\State \textbf{goto} \emph{loop}.
%\State \textbf{close};
%\EndIf
%\State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
%\State \textbf{goto} \emph{top}.
%\EndProcedure
%\end{algorithmic}
%\end{algorithm}
